
\section{Developing Unikernel Applications}

Since Unikernel first introduced in 2013 by Madhavapeddy et al in \cite{library-operating-system}, there has been different language stacks to implement the proposed solution. Table \ref{tab:stacks} shows couple of state of the art projects with their target platform and their respective development language.

\begin{table}[htpb]
    \caption[Different Unikernel Stacks]{Different Unikernel Stacks}\label{tab:stacks}
    \centering
    \begin{tabular}{ |c |c |c| }
      \toprule
        Unikernel & Language & Target \\
      \midrule
        MirageOS & OCaml & KVM,Xen, RTOS \\
        \hline
        OSv & Java,C,Node,Ruby & Virtualbox,KVM,Google Cloud, AWS,ESXi \\
        \hline
        HalVM & Haskell & Xen \\
      \hline
        Rumprun & C,C++, Erlang,... &  Xen, KVM \\
      \bottomrule
    \end{tabular}
  \end{table}

The reason for choosing MirageOS was the activity around its development and that it behaves directly as a unikernel. For example, both OSv and Rumprun have unused functionality on their kernels to support more languages.

MirageOS requires two files to develop a unikernel. First one is the \textit{config.ml} file. It defines the entry point of the program and lists dependencies. Second one is \textit{unikernel.ml} , which has the application entry point. To use a dependency, it has to be in the config file and adding a dependency requires additional files to be regenerated.

MirageOS uses an OPAM package with the name \textit{mirage} \cite{opammirage} for development. This package is used to create configuration files that will be sealed with the application code for the target environment and it also compiles the application. Drivers for unikernels are also written in OCaml and published as additional opam packages. Once Mirage creates a deployment tree, it installs required packages through the OCaml repository. The following command in \ref{fig:mirage_configure} configures a package for compilation.

\begin{code}[htpb]
    \centering
    \begin{tabular}{c}
    \begin{lstlisting}[language=bash]
      mirage configure --target hvt --kv_ro direct
  \end{lstlisting}
  \end{tabular}
  \caption{Generating unikernel specific files}\label{fig:mirage_configure}
\end{code}

That command targets the solo5 environment with \textit{hvt} value. \textit{kv\_ro} is a project specific flag, which tells unikernels to access the underlying file system directly to read key-value store. After that step a \textit{Makefile} is generated for future commands. \textit{make depend} downloads dependencies for the program and \textit{make build} builds the unikernel. Build command compiles and seals the unikernel in couple of seconds, once the dependencies are installed. The build artifact is a single image. If it requires static files during build, they can either be packaged into the image or the image can be configured to access them during runtime. This choice has to be specified during compile time because MirageOS installs different drivers depending on usage.
